---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# GeNPF

<!-- badges: start -->
<!-- badges: end -->

The goal of General Purpose Functions (GeNPF) is to offer user define functions for a seamless yet standardized workflow for working with data between google bucket and Terra persistent disk within Institute of Molecular and Computational Medicine (IMCM).

The main goal of {GeNPF} is to achieve a painless pull and push of data between workspaces and Rstudio interactive environment, saving time for analysis and data exploration. It's a wrapper around `gsutil` and other tools to work with data in the cloud.


## Installation

You can install the development version of GeNPF from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("cmaronga/GeNPF")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(GeNPF)
## basic example code

```

